Development of User-Friendly\\System Identification Techniques

### 2016-02-16 front-and-back-matter/titlepages.tex
Update VUB title page
Update title page + summary

%\promotortitle{Promotor/Promotors}
\promotor{
  \jurymember{prof. dr. ir.}{Johan Schoukens}{Vrije Universiteit Brussel}
  \jurymember{dr. ir.}{Tom Oomen}{Eindhoven University of Technology}
}

\title{Development of User-friendly\\System Identification Techniques}

@@

\jury{
  \jurymember{prof. dr. ir.}{Keith R. Godfrey}{Warwick University}
  \jurymember{prof. dr. ir.}{Tomas McKelvey}{Chalmers}
  \jurymember{dr. ir.}{Bart Peeters}{LMS}
  \jurymember[president]{prof. dr. ir.}{Johan Deconinck}{Vrije Universiteit Brussel}
  \jurymember[secretary]{dr. ir.}{Koen Tiels}{Vrije Universiteit Brussel}
}

>>>>

%\promotortitle{Promotor/Promotors}
\promotor{
  \jurymember{prof. dr. ir.}{Johan Schoukens}{Vrije Universiteit Brussel (VUB)}
  \jurymember{dr. ir.}{Tom Oomen}{Eindhoven University of Technology}
}

\title{Development of User-Friendly\\System Identification Techniques}

@@

\jury{
  \jurymember[president]{prof. dr. ir.}{Johan Deconinck}{VUB -- ETEC}
  \jurymember[vice-president]{prof. dr. ir.}{Patrick Guillaume}{VUB -- MECH}
  \jurymember[secretary]{dr. ir.}{Koen Tiels}{VUB -- ELEC}
  \jurymember{prof. dr. ir.}{Keith R. Godfrey}{University of Warwick}
  \jurymember{prof. dr. ir.}{Tomas McKelvey}{Chalmers University of Technology}
  \jurymember{dr. ir.}{Bart Peeters}{Siemens Industry Software -- LMS}
}
